\documentclass[12pt,letterpaper]{article}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{pslatex}
\usepackage{url}
\usepackage{paralist}
\usepackage{enumitem}
\usepackage{longtable}
%\usepackage{etaremune}

% Set your name here
\def\name{Laura R. Kreidberg}

\geometry{
  body={6.5in, 9.5in},
  left=1.0in,
  top=1.0in,
  bottom = 1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Don't indent paragraphs.
\setlength\parindent{0em}

\renewenvironment{itemize}{
	\begin{list}{}{
	\setlength{\leftmargin}{1mm}%
	\setlength{\itemsep}{0pt}%
	\setlength{\parskip}{0pt}
	}
}{
	\end{list}
}

\begin{document}
\sloppy

% Place name at left
%{\LARGE \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{3 mm}

\begin{tabular}{@{}p{4.0in}@{}p{5.0in}}
    \LARGE{Laura Kreidberg}                  & E-mail: kreidberg@mpia.de\\  
    \,                                       & http://www.cfa.harvard.edu/$\sim$lkreidberg \\ 
    \large{Curriculum vitae} (April 2020) & \, \\
\end{tabular}
\vspace{8mm}

\textbf{\textsc{Appointments}}\\
%Assistant Professor, Leiden Observatory \hfill beginning 2020\\
Director, APEx Department, Max Planck Institute for Astronomy \hfill 2020 - present \\
Clay Fellow, Harvard-Smithsonian Center for Astrophysics \hfill 2019 - 2020\\
Junior Fellow, Society of Fellows, Harvard University \hfill 2016 - 2019\\
ITC Fellow, Harvard University \hfill 2016 - 2019\\

\textbf{\textsc{Education}}
\vspace{-2mm}
\begin{itemize}
    \item \textbf{University of Chicago}, Ph.D. Astronomy and Astrophysics \hfill 2016
    \item \textbf{Yale University} B.S. Physics and Astronomy, with distinction \hfill 2011
\end{itemize}

\vspace{5mm}
\textbf{\textsc{Fellowships and Awards}}
\begin{compactitem}[]
\item Paul Hertelendy (pH) Lecturer, Harvard-Smithsonian Center for Astrophysics \hfill 2018 
\item International Astronomical Union Division F PhD Prize \hfill 2017
\item Hubble and Sagan Postdoctoral Fellowships (both declined) \hfill 2016
\item Rodger Doxsey Travel Prize, American Astronomical Society \hfill 2016
\item William Rainey Harper Dissertation Fellowship, University of Chicago \hfill 2015
\item Peter B. Wagner Memorial Award for Women in Atmospheric Sciences \hfill 2015
\item Plotnick Fellowship, University of Chicago Physical Sciences Division \hfill 2015
\item National Science Foundation Graduate Research Fellowship \hfill 2013 - 2016
\item Illinois Space Grant Fellowship \hfill 2012
\item George Beckwith Prize for excellence in astronomy, Yale Astronomy Department \hfill2011
\end{compactitem}
\vspace{6mm}

\textbf{\textsc{Refereed Publications}} (2415 total citations)\\
\vspace{1mm}
\hspace*{5mm}First author and papers led by students: \\
\hspace*{5mm}(*** denotes student papers supervised by L.K.)\\
\hspace*{5mm}($\star$ denotes equal author contribution)
\begin{compactenum}
\item ``Absence of a thick atmosphere on the terrestrial exoplanet LHS 3844b"\\ 
\textbf{Kreidberg}, Koll$^\star$, Morley$^\star$, Hu$^\star$, et al., Nature, 573, 87 
                                                                                
\item ``No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System"\\
\textbf{Kreidberg}, Luger, and Bedell, ApJL, 877, 15

\item``The Sub-Neptune Desert and Its Dependence on Stellar Type: Controlled by Lifetime X-Ray Irradiation"\\
****McDonald, \textbf{Kreidberg}, and Lopez, ApJ, 876, 22

\item ``Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103b from HST and Spitzer Phase Curve Observations"\\
\textbf{Kreidberg}, Line, Parmentier et al., 2018, \textit{AJ}, 156, 17

\item ``SPIDERMAN: an open-source code to model phase curves and secondary eclipses"\\
****Louden and \textbf{Kreidberg} 2018, MNRAS, 477, 2613 

\item ``Water, High Altitude Condensates, and Possible Methane Depletion in the Atmosphere of the Warm Neptune WASP-107b"\\
\textbf{Kreidberg}, Line, Thorngren et al. 2018, ApJL, 858, 6 

\item ``Exoplanet Atmosphere Measurements from Transmission Spectroscopy and other Planet-Star Combined Light Observations"\\
\textbf{Kreidberg} 2017, Handbook of Exoplanets,  arXiv:1709.05941

\item ``Prospects for Characterizing the Atmosphere of Proxima Centauri b"\\
\textbf{Kreidberg} \& Loeb, 2016, \textit{ApJL}, 832, 12 

\item ``A Detection of Water in the Transmission Spectrum of the Hot Jupiter WASP-12b and Implications for its Atmospheric Composition"\\
\textbf{Kreidberg}, Line,  Bean, et al., 2015, \textit{ApJ}, 814, 66

\item ``\texttt{batman}: BAsic Transit Model cAlculatioN in Python"\\
\textbf{Kreidberg} 2015, \textit{PASP}, 127, 1161 

\item ``A Precise Water Abundance Measurement for the Hot Jupiter WASP-43"\\
\textbf{Kreidberg}, Bean, D\'esert, et al. 2014, \textit{ApJL}, 793, 27

\item ``Clouds in the Atmosphere of the Super-Earth Exoplanet GJ 1214b"\\
\textbf{Kreidberg}, Bean, D\'esert, et al. 2014, \textit{Nature}, 505, 69

\item ``Mass Measurements of Black Holes in X-Ray Transients:  Is There a Mass Gap?"\\
\textbf{Kreidberg}, Bailyn, Farr, \& Kalogera 2012, \textit{ApJ}, 757, 36
\end{compactenum}

\vspace{3mm}
\hspace*{5mm}Co-authored:
\begin{compactenum}
\setcounter{enumi}{13}
\item ``A sub-Neptune exoplanet with a low-metallicity methane-depleted atmosphere and Mie-scattering clouds"\\
    Benneke, Knutson, Lothringer, et al. [including \textbf{Kreidberg}], 2019, Nature Astronomy, in press

\item ``TESS Spots a Compact System of Super-Earths around the Naked-eye Star HR 858"\\
    Vanderburg, Huang, Rodriguez, et al. [including \textbf{Kreidberg}], 2019, ApJ, 881, 19

\item ``Climate of an Ultra hot Jupiter: Spectroscopic phase curve of WASP-18b with HST/WFC3"\\
    Arcangeli, D\'esert, Parmentier, et al. [including \textbf{Kreidberg}], 2019, A\&A, 625, 136

\item ``The L 98-59 System: Three Transiting, Terrestrial-Sized Planets Orbiting a Nearby M-dwarf"\\
    Kostov, Schlieder, Barclay, et al. [including \textbf{Kreidberg}], 2019, AJ, 158, 32

\item ``HD 202772A b: A Transiting Hot Jupiter around a Bright, Mildly Evolved Star in a Visual Binary Discovered by TESS"\\
    Wang, Jones, Shporer, et al. [including \textbf{Kreidberg}], 2019, AJ, 157, 51

\item ``Detection of Helium in the Atmosphere of the Exo-Neptune HAT-P-11b"\\
Mansfield, Bean, Oklop\v{c}i\'{c}, \textbf{Kreidberg}, et al. 2018, ApJL, 868, 34

\item ``A Framework for Prioritizing the TESS Planetary Candidates Most Amenable to Atmospheric Characterization"\\
   Kempton, Bean, Louie, et al. [including \textbf{Kreidberg}], 2018, PASP, 130, 4401 

\item  ``The Transiting Exoplanet Community Early Release Science Program for \textit{JWST}"\\
    Bean, Stevenson, Batalha, et al. [including \textbf{Kreidberg}], 2019, PASP, 130, 993 

\item ``Helium in the eroding atmosphere of an exoplanet"\\
    Spake, Sing, Evans, et al. [including \textbf{Kreidberg}] 2018, \textit{Nature}, 557, 68

\item ``From thermal dissociation to condensation in the atmospheres of extremely hot Jupiters: WASP-121b into context"\\
	Parmentier, Line, Bean, et al. [including \textbf{Kreidberg}], 2018, \textit{A\&A}, 617, 110

\item ``Two Warm, Low-Density Sub-Jovian Planets Orbiting Bright Stars in K2 Campaigns 13 and 14"
	Yu, Rodriguez, Crossfield, et al. [including \textbf{Kreidberg}], 2018, \textit{AJ}, 156, 127 

\item ``A HST/WFC3 Thermal Emission Spectrum of the Hot Jupiter HAT-P-7b"\\
Mansfield, Bean, Line, et al. [including \textbf{Kreidberg}], 2018, \textit{AJ}, 156, 10

\item ``H- Opacity and Water Dissociation in the Dayside Atmosphere of the Very Hot Gas Giant WASP-18b"\\
	Arcangeli, D\'{e}sert, et al. [including \textbf{Kreidberg}] 2018, \textit{ApJL}, 855, 30 

\item ``An ultra-short period rocky super-Earth with a secondary eclipse and a Neptune-like companion around K2-141"\\
Malavolta, Mayo, et al. [including \textbf{Kreidberg}] 2018, \textit{AJ}, 155, 107 

\item ``Observing the Atmospheres of Known Temperate Earth-sized Planets with JWST"\\
Morley, \textbf{Kreidberg}, et al. 2017, ApJ, 850, 121 

\item ``Trends in Atmospheric Properties of Neptune-Size Exoplanets"\\
Crossfield and \textbf{Kreidberg} 2017, \textit{AJ}, 154, 261 

\item ``Quantifying the Impact of Spectral Coverage on the Retrieval of Molecular Abundances from Exoplanet Transmission Spectra"\\
Chapman, Zellem, Line, et al. [including \textbf{Kreidberg}] 2017, \textit{PASP}, 129, 980

\item ``Determining Empirical Stellar Masses and Radii Using Transits and Gaia Parallaxes as Illustrated by Spitzer Observations of KELT-11b"\\
Beatty, Stevens, Collins, et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 154, 25 

\item ``A Multi-planet System Transiting the V = 9 Rapidly Rotating F-Star HD 106315"\\
Rodriguez, Zhou, Vanderburg, et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 153, 256

\item ``HELIOS: An Open-Source, GPU-Accelerated Radiative Transfer Code for Self-Consistent Exoplanetary Atmospheres"\\
Malik, Grosheintz,  et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 153, 56 

\item ``Spitzer Phase Curve Constraints for WASP-43b at 3.6 and 4.5 microns"\\
Stevenson, Line, Bean, et al. [including \textbf{Kreidberg}] 2016, \textit{AJ}, 153, 68 

\item ``Near-IR Emission Spectrum of WASP-103b using Hubble Space Telescope/Wide Field Camera 3"\\
Cartier, Beatty, Zhao, et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 153, 34


\item ``No Thermal Inversion and a Solar Water Abundance for the Hot Jupiter HD 209458b from HST WFC3 Emission Spectroscopy"\\
Line, Stevenson, Bean, et al. [including \textbf{Kreidberg}], 2016, \textit{AJ}, 152, 203 

\item ``The Impact of Non-uniform Thermal Structure on the Interpretation of Exoplanet Emission Spectra"\\
Feng, Line, Fortney, et al. [including \textbf{Kreidberg}], 2016, \textit{ApJ}, 829, 52

\item ``Transiting Exoplanet Studies and Community Targets for JWST's ERS Program"\\
Stevenson, Lewis, Bean, et al. [including \textbf{Kreidberg}], 2016, \textit{PASP}, 128, 967 

\item ``The Atmospheric Circulation of the Hot Jupiter WASP-43b" \\
Kataria, Showman, Fortney, et al. [including \textbf{Kreidberg}] 2015, \textit{ApJ}, 801, 86

\item ``Observations of Transiting Exoplanets with the James Webb Space Telescope (JWST)"\\
Beichman, Benneke, Knutson, et al. [including \textbf{Kreidberg}] 2014, \textit{PASP}, 126, 1134

\item ``Thermal structure of an exoplanet atmosphere from phase-resolved emission spectroscopy"\\
Stevenson, D\'esert, Line, et al. [including \textbf{Kreidberg}] 2014, \textit{Science}, 346, 838

\item ``A Hubble Space Telescope Search for a Sub-Earth-sized Exoplanet in the GJ 436 System"\\
Stevenson, Bean, Fabrycky, \& \textbf{Kreidberg} 2014, \textit{ApJ}, 796, 32

\item ``HST Near-IR Transmission Spectroscopy of the Super-Earth HD 97658b"\\
Knutson, Dragomir, \textbf{Kreidberg}, et al. 2014, \textit{ApJ}, 794, 155

\item ``Transmission Spectroscopy of the Hot Jupiter WASP-12b from 0.7 to 5 $\mu$m"\\
Stevenson, Bean, Seifahrt, et al. [including \textbf{Kreidberg}] 2014, \textit{AJ}, 147, 161

\item ``The Mass Distribution of Stellar-Mass Black Holes"\\
Farr, Sravan, Cantrell, \textbf{Kreidberg} et al. 2011, \textit{ApJ}, 741, 103
\end{compactenum}
\vspace{4mm}

\textbf{\textsc{White Papers and Research Notes}} 
\vspace{1mm}
\begin{compactenum}
\item ``Non-Detection of a Helium Exosphere for the Hot Jupiter WASP-12b"\\
\textbf{Kreidberg} and Oklop\v{c}i\'{c} 2018, \textit{RNAAS}, 2, 44

\item ``Understanding Stellar Contamination in Exoplanet Transmission Spectra as an Essential Step in Small Planet Characterization"\\
Apai, Rackham, et al. [including \textbf{Kreidberg}] 2018, submitted to the National Academy of Sciences Committee on Exoplanet Science Strategy, arXiv:1803.08708

\item ``Additional Exoplanet Science Enabled by FINESSE"\\
Zellem, Fortney, et al. [including \textbf{Kreidberg}] 2018, submitted to the
National Academy of Sciences Committee on Exoplanet Science Strategy, arXiv:1803.07163

\item ``The Science Case for an Extended Spitzer Mission"\\
Yee, Fazio, et al. [including \textbf{Kreidberg}] 2017, arXiv:1710.04194
\end{compactenum}




\vspace{5mm}
\textbf{\textsc{Invited Talks}} 
\begin{compactitem}[]
\item {UC Berkeley Astronomy Colloquium \hfill 12/2020}
\item {EPSC Exoplanet Keynote (virtual) \hfill 09/2020}
\item {AG2020 Splinter Session: Exploring the Diversity of Exoplanets (virtual) \hfill 09/2020}
\item {UCL Exoplanet Seminar (virtual) \hfill 04/2020}
\item {Astrophysics Colloquium (virtual), Oxford University \hfill 04/2020}
\item {Physics Colloquium, Stony Brook University \hfill 03/2020}
\item {EPS Colloquium, Harvard University \hfill 03/2020}
\item {Lecture, Future Directions in Solar, Stellar and Planetary physics, NYU Abu Dhabi \hfill 01/2020}
\item {Review Talk, ARIEL Open Science Conference \hfill 01/2020} 
\item {AAS Meeting 235, Special Session: Spitzer's Scientific Legacy \hfill 01/2020}
\item {Overview Talk, Rocky Planets in the Era of JWST \hfill 11/2019}
\item {Seminar, Nieman Foundation for Journalism, Harvard \hfill 09/2019}
\item {Munich Joint Astronomy Colloquium \hfill 05/2019}
\item {Astronomy Colloquium, Leiden Observatory \hfill 04/2019}
\item {Special Seminar, Institute of Astronomy, Cambridge \hfill 03/2019}
\item {APS Department Colloquium, University of Colorado Boulder \hfill 02/2019}
\item {Special Seminar, Space Telescope Science Institute \hfill 01/2019}
\item {Astronomy Colloquium, UT Austin \hfill 11/2018}
\item {Lecture the Radcliffe Institute Symposium ``The Undiscovered" \hfill 10/2018}
\item {Lecture at Multi-Dimensional Characterization of Distant Worlds, U. Michigan \hfill 10/2018}
\item {Lecture at Cloud Academy, Les Houches, France \hfill 09/2018} 
\item {Big Data Conference, Harvard Center of Mathematical Sciences and Application \hfill 08/2018}
\item {K\"{a}ll\'{e}n Symposium, Lund Observatory, Sweden \hfill 05/2018}
\item {Astronomy Colloquium, Yale University \hfill 04/2018}
\item{Astronomy Colloquium, Harvard University \hfill 03/2018}
\item {AAS Meeting 231, Special Session: A Roadmap to Detecting Biosignatures \hfill 01/2018}
\item {Koenigstuhl Colloquium, Max Planck Institute for Astronomy \hfill 12/2017}
\item {School of Earth and Space Exploration Seminar, Arizona State University \hfill 11/2017}
\item {Habitable Worlds Conference, M-Dwarf breakout session \hfill 11/2017}
\item {Astrophysics Seminar, Brown University \hfill 10/2017}
\item {Astrophysics Seminar, University of Massachussetts Lowell \hfill 10/2017}
\item {Astronomy Colloquium, University of Michigan \hfill 09/2017}
\item {Astronomy Seminar, Michigan State University \hfill 09/2017}
\item {Review Talk, Transiting Exoplanets Conference, Keele, UK \hfill 07/2017}
\item {Invited Talk, Enabling Transiting Exoplanets with JWST Workshop, Baltimore, MD \hfill 07/2017}
\item {Astronomy Colloquium, University of California Santa Cruz \hfill 05/2017}
\item {Seminar, Southwest Research Institute \hfill 05/2017}
\item {Invited Talk, Breakthrough Discuss Conference \hfill 04/2017}
\item {Astronomy Seminar, American Museum of Natural History, NY \hfill 04/2017}
%\item {Invited Talk, Atmospheres of Disks and Planets 2017, Ringberg, Germany \hfill 04/2017}
\item {Astronomy Colloquium, University of Illinois at Urbana-Champaign \hfill 03/2017}
\item {Astronomy Colloquium, The Ohio State University \hfill 02/2017}
\item {Planetary Seminar, Georgia Institute of Technology \hfill 11/2016}
\item {ITC Lunch, Harvard University \hfill 10/2016}
\item {Opportunity M, Harvard University \hfill 08/2016}
\item {Center for Space and Habitability Colloquium, University of Bern \hfill 04/2016}
\item {Grinnell Physics Department Seminar \hfill 02/2016}
\item {Astronomy Department Colloquium, Columbia University \hfill 12/2015}
%\item {Astro Tuesday Chalk Talk, U. Chicago \hfill 09/2015}
%\item {SciFoo Camp; led session on ``Prospects for Detecting Alien Life" \hfill 06/2015}
\item {Harvard Center for Astrophysics SSP Seminar \hfill 02/2015}
\item {225th AAS special session: ``From Hot Jupiters to Scorched Earths" \hfill 01/2015}
%\item {Gemini Planet Imager collaboration meeting \hfill 09/2014}
%\item {Chicago Center for Cosmochemistry \hfill 04/2014}
%\item {Planning Meeting on Transit Observing with JWST\hfill 03/2014}
%\item {Exoclimes IV, Squamish, BC \hfill 08/2016}
%\item {Exoplanets I, Davos, Switzerland \hfill 06/2016}
%\item {AstroChicago123, invited panelist for ``Exoplanets in 2042" debate \hfill 011/15}
%\item {Emerging Researchers in Exoplanets Symposium; contributed talk and invited panelist \hfill 05/2015}
%\item {Hubble Space Telescope IV; poster \hfill 03/2014}
%\item {Exoclimes III; contributed talk \hfill 02/2014}
%\item {223rd AAS Meeting; contributed talk and press conference presentation \hfill 01/2014}
%\item {Protostars and Planets VI; poster \hfill 07/2013}
%\item {221st AAS Meeting; contributed talk \hfill 01/2013}
%\item {220th AAS Meeting; poster \hfill 05/2012}
%\item {215th AAS Meeting; poster \hfill 01/2010}
\end{compactitem}


\vspace{4mm}
\textbf{\textsc{Accepted Observing Proposals}} \textsc{(as PI)}
\vspace{1mm}

\begin{tabular}{ l p{5.0cm} p{10cm}}
  %\textbf{Date} & \textbf{Facility} & \textbf{Time} & \textbf{Title}\\
  2018 & \textit{Spitzer}: 100.9\,hrs, PID 14204 & ``A Test for the Existence of an Atmosphere on a Terrestrial Exoplanet 
    Orbiting a Small Star"\\
  2018 &  \textit{Spitzer}: 65.7\,hrs, PID 14135 & ``Taking the Temperature of a Lava Planet"\\
  2017 &  \textit{HST}: 127\,orbits, GO 15333& ``Atmospheric Diversity of Mini-Neptunes in Multi-planet Systems" (co-PI with I. Crossfield)\\
  2017 &  \textit{HST}: 6\,orbits, GO 15110& ``A Study of the UV Environment for Three Small Planets Transiting a Nearby M-Dwarf" \\
  2017 &  \textit{HST}: 5\,orbits, GO 15109& ``Caught Red-Handed: A Novel Search for the Culprit Behind Thermal Inversions in Exoplanet Atmospheres" \\
  2017 &  \textit{HST}: 9\,orbits, GO 15255& ``The KELT-11b Opportunity: Atmospheric Water Abundance for a Sub-Saturn-Mass Planet" (co-PI with K. Colon)\\
 2017 & \textit{HST}: 5\,orbits, GO 14915 & ``First Atmosphere Characterization of the Benchmark Exo-Neptune WASP-107b"\\
 2017 & \textit{Spitzer}: 15\,hours, PID 13167& ``First Atmosphere Characterization of the Benchmark Exo-Neptune WASP-107b"\\
2016 & \textit{Spitzer}: 132\,hrs, PID 13140 \textit{HST}: 3 orbits, GO 14843 & ``Clouds in the Forecast? A Joint Spitzer and HST Investigation of Clouds and Hazes for Two Exo-Neptunes"\\
2014 & \textit{Spitzer}: 134\,hrs, PID 11099 \textit{HST}: 30 orbits, GO 14050& ``Exploring the Frontier of Exoplanet Atmosphere Dynamics with NASA's Great Observatories"
\end{tabular}
%\item ``FINESSE: Fast Infrared Exoplanet Spectroscopy Survey Explorer"\\
%Submitted 12/2016 to the NASA MIDEX AO (CoI: Kreidberg)
%Spitzer funding = 10k; HST funding = $136,567
%\item ``The Newest Hot Jupiter Archetype Through the Eyes of NASA's Great Observatories" \\
%\textit{Spitzer} Cycle 11 Program 11001; 26 hours (PI K. Stevenson) \hfill 12/2014 
%\item ``Follow the Water: The Ultimate WFC3 Exoplanet Atmosphere Survey"\\
% \textit{HST} Cycle 21 Program 13467; 150 orbits (PI J. Bean) \hfill 05/2013
%\item ``The Abundance of Water in the Atmosphere of the Super-Earth Archetype GJ\,1214b"\\
%\textit{Gemini} DD Program 2013A-DD-1; 24 hours $[$partial completion$]$ \hfill 02/2013 
%SMARTS

\vspace{3mm}
%\textbf{\textsc{Observing Experience}} 
%\begin{compactitem}[]
%\item Magellan/IMACS, 1 night \hfill 03/2015
%\item Magellan/MMIRS, 3 nights \hfill 05/2014
%\item Magellan/IMACS, 1 night \hfill 12/2013
%\item Magellan/IMACS, 1 night \hfill 10/2013
%\item Gemini South/Flamingos2, 1 night of queue observing \hfill 10/2013
%\item Gemini North/GMOS, 2 nights of queue observing \hfill 05/2013
%\end{compactitem}
%\vspace{5mm}

\vspace{3mm}
\textbf{\textsc{Service}} 
\begin{compactitem}[]
%\item Student Representative to Physical Science Division disciplinary hearing \hfill 2015
%\item Chair, MIRI Working Group, JWST ERS proposal \hfill 2017
% AAS Chambliss Judge, session chair
\item {Science Organizing Committee member, Exoplanets III \hfill 2018 - present}
\item {External reviewer for ERC Consolidator grants \hfill 2019}
\item {Kavli Foundation, AGU/AAS workshop on Accelerating the Future of Exoplanet Science\hfill 2019}
\item {HST-TESS Advisory Committee member \hfill 2019}
\item {Member, TESS Follow-Up Network SG5 (Space-Based Photometry) \hfill 2018 - present}
\item {Target selection lead of the TESS Atmosphere Characterization Working Group \hfill 2018 - present}	
\item {Member of the science team for ARIEL, a medium-class atmosphere\newline characterization mission recently selected by ESA \hfill 2016-present}
\item {Chair of the MIRI working group and member of the science council for the \newline JWST Transiting Exoplanet Community Early Release Science Program \hfill 2017- present}
\item{HST Cycle 27 Panel Reviewer}
\item {Member of the science team for FINESSE, a candidate Explorer-class atmosphere\newline characterization mission \hfill 2016-2018}
\item {Spitzer Cycle 14 Panel Reviewer \hfill 2018}
\item {Reviewer for Hubble Mid-Cycle Proposals \hfill 2017, 2018, 2019}
\item {Member of the Breakthrough Starshot science team \hfill 2016 - present}
\item Reviewer for NASA Exoplanet Research Program (XRP) proposals \hfill	2016
\item Reviewer for NASA Earth and Space Science Fellowship \hfill 2016
\item Referee for ApJ, AJ, ApJL, MNRAS, Nature, Nature Astronomy, PASP \hfill 2015 - present
\item Student representative, Undergraduate Curriculum Committee \hfill 2014 - 2015
\item Student representative, Dean's Student Advisory Committee \hfill 2013 - 2015
\item Co-organizer, Exoplanet Journal Club \hfill 2013 - 2014
\item Speaker Engagement Coordinator for colloquia \hfill 2012 - 2013
\item Student representative, Brinson Lectureship Committee \hfill 2012, 2014
\end{compactitem}


\vspace{7mm}
\textbf{\textsc{Teaching and Mentoring}} 
\begin{compactitem}[]
%\item Supervisor, for graduate students Tom Louden and George McDonald at Kavli Program on Exoplanet Atmospheres \hfill 2016
%\item Supervisor, for undergraduate student (Lily Zhao) on \textit{HST}/STIS research project  \hfill 2015-2016
\item Students advised  (*** denotes primary thesis advisor)
	\begin{compactitem}
        \item Sebastian Zieba***, graduate student at Leiden \hfill beginning 2020
		\begin{sloppypar}
		Taking the Temperature of a Lava Planet: A Phase Curve of K2-141b
		\end{sloppypar}
        \item Hannah Diamond-Lowe, graduate student at Harvard \hfill 2018 - present
		\begin{sloppypar}
		Planet Atmospheres in Rocky-to-Gaseous Transition: a K2-3 Case Study
		\end{sloppypar}
	\item Tom Louden, graduate student at Kavli Program in Astrophysics \hfill 2016 - 2018
		\begin{sloppypar}
		Project: \textit{``SPIDERMAN: a fast code to map the surfaces of exoplanets"}
		\end{sloppypar}
	\item George McDonald, graduate student at Kavli Program in Astrophysics \hfill 2016-2018
		\begin{sloppypar}
		Project: \textit{``Exploring the super-Earth desert"}
		\end{sloppypar}
	\item Lily Zhao, U. Chicago undergraduate \hfill 2015 - 2016
		\begin{sloppypar}
		Project: \textit{``HST/STIS transmission spectroscopy for the hot Jupiter WASP-12b"}
		\end{sloppypar}
	\end{compactitem}
%\hspace*{5 mm} Tom Louden, graduate student at Kavli Program on exoplanet atmospheres \hfill 2016\\
%\hspace*{5 mm} George McDonald, graduate student at Kavli Program on exoplanet atmospheres \hfill 2016\\
%\hspace*{5 mm} Lily Zhao, U. Chicago undergraduate \hfill 2015 - 2016\\
%\item Guest lecturer, Princeton University, Journalism 
\item Guest lecturer, Harvard University, ``Exoplanets" graduate course \hfill 2018
\item Mentor, U. Chicago MGC Mentoring Program \hfill 2014-2016 
\item Mentor, U. Chicago Women in Physics and Astronomy \hfill2014-2015
\item Guest lecturer, DePaul University ``Science and SETI" course \hfill2015, 2016
\item Teaching Assistant, University of Chicago
	\begin{compactitem}
	\item Astronomy 282:  Exoplanets \hfill 2013
	\item Physical Science 119:  Stellar Astronomy	\hfill 2012
	\item Astronomy 241:  Physics of Stars and Stellar Systems \hfill	2011 
	\end{compactitem}
%\item Peer Tutor, Yale Physics Department \hfill 2010-2011
%\item Physics and Astronomy Tutor, Yale College Dean's Office \hfill 2009 -- 2011
\end{compactitem}

%\vspace{3mm}
%\textbf{\textsc{Press}} 
%Scientific American, Finnish Space Magazine, NYT, Time, NPR
%work featured in Hubble Science Year in Review (2014?)
%work featured in Time Magazine special issue "The Search for Life in the Universe"
%YouTube videos


%\vspace{3mm}
%\textbf{\large Big Projects}
%\begin{compactitem}[]
%\item Templeton proposal from Dave
%\item FINESSE/CASE
%\item JWST ERS
%\end{compacitem}

%\textbf{\large Workshops}
%\begin{itemize}
%\item Sagan Exoplanet Summer Workshop \hfill July 2014
%\item JWST Planning Workshop \hfill March 2014
%\item Chandra X-Ray Binary Conference \hfill July 2012
%\item Sagan Exoplanet Summer Workshop \hfill July 2012
%\end{itemize}

%\vspace{3mm}

%\textbf{\large Skills}
%Programming Languages:  C, R (fluent); IDL, Python, Fortran (conversational)

\vspace{7mm}

\textbf{\textsc{Outreach}} 
\begin{compactitem}[]
\item Co-founder, Astronomy on Tap Chicago \hfill 2016
\item Research featured in an episode of PBS's \href{https://www.youtube.com/watch?v=i4Hrmh6LJ0Q&index=2&list=PLsRLUurFnvvXTEbTjA1tvHhWmh6aKTgDw}{``The Good Stuff"} (30k views) \hfill 11/2015
\item Public lecture on ``Prospects for Detecting Alien Life in the Next Decade" \hfill 2014-2018 \\
\hspace*{5 mm}delivered over 10 times
\item Invited panelist, PyLadiesChicago discussion on Python in scientific research \hfill 04/2015
\item Press coverage includes \href{http://science.time.com/2013/12/31/the-real-space-oddities-super-earths-and-jumbo-neptunes/}{Time}, \href{http://www.nature.com/scientificamerican/journal/v23/n3s/full/scientificamericanuniverse0814-4.html}{Scientific American}, \href{http://www.npr.org/2014/01/02/259222620/on-planet-gj1214-b-expect-exotic-cloud-cover}{NPR}, \href{http://news.nationalgeographic.com/news/2014/10/141014-space-hubble-planet-weather-science/?utm_source=Twitter&utm_medium=Social&utm_content=link_tw20141014news-hubbletele&utm_campaign=Content&sf5218387=1}{National Geographic} \hfill 2013 - present
\item Participant in \href{https://www.youtube.com/watch?v=n-oDqYCf3XY}{Hubble Hangout: The Thermal Map of Exoplanet WASP-43b} \hfill 11/2014
\item YouTube video ``\href{https://www.youtube.com/watch?v=tQZqAVhUk9E}{A Weather Map for the Hot Jupiter WASP-43b}" (5k views) \hfill 10/2014
\item YouTube video ``\href{https://www.youtube.com/watch?v=8x2DcgZiKTA}{Clouds on the Super-Earth Exoplanet GJ 1214b}" (30k views) \hfill 12/2013
%	\hspace*{10 mm} ORD Camp, Chicago \hfill 01/2015 \\
%	\hspace*{10 mm} Truborn Gallery Art of Science series \hfill 12/2014 \\
%	\hspace*{10 mm} Renaissance Court Senior Center \hfill 12/2014 \\
%	\hspace*{10 mm} Carl Sagan Day; University of Chicago Secular Alliance \hfill 11/2014\\
%	\hspace*{10 mm} The Roycemore School \hfill 05/2014\\
%	\hspace*{10 mm} Harbor Point Senior Center \hfill 03/2014
%\item{Web:}\\
%	\hspace*{10 mm} Participant in Hubble Hangout: The Thermal Map of Exoplanet WASP-43b \hfill 11/2014\\
%	\hspace*{10 mm} YouTube video ``A Weather Map for the Hot Jupiter WASP-43b" (4k views) \hfill 10/2014\\
%	\hspace*{10 mm} YouTube video ``Clouds on the Super-Earth Exoplanet GJ 1214b" (14k views) \hfill 12/2013
\item Invited panelist, Northeast Conference for Undergraduate Women in Physics \hfill 01/2012
%\item Science fair prep at St. Thomas the Apostle \hfill 10/2014
%\item Undergraduate Mentor, Women in Science at Yale \hfill 2010 -- 2011
%\item Organizing Committee Member, Northeast Conference for Undergraduate\\
%\hspace*{10mm} Women in Physics \hfill 2009 -- 2011
\end{compactitem}


\end{document}
