\documentclass[12pt,letterpaper]{article}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{pslatex}
\usepackage{url}
\usepackage{paralist}
\usepackage{enumitem}
%\usepackage{etaremune}

% Set your name here
\def\name{Laura R. Kreidberg}

\geometry{
  body={6.5in, 9.5in},
  left=1.0in,
  top=1.0in,
  bottom = 1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Don't indent paragraphs.
\setlength\parindent{0em}

\renewenvironment{itemize}{
	\begin{list}{}{
	\setlength{\leftmargin}{1mm}%
	\setlength{\itemsep}{0pt}%
	\setlength{\parskip}{0pt}
	}
}{
	\end{list}
}

\begin{document}
\sloppy

% Place name at left
{\LARGE \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{3 mm}

\begin{tabular}{@{}p{4.0in}@{}p{5.0in}}
Harvard Astronomy Department         & Phone: (775) 233-7497 \\
60 Garden Street                     & E-mail: laura.kreidberg@cfa.harvard.edu\\ 
Cambridge, MA 02138                  & http://www.cfa.harvard.edu/$\sim$lkreidberg \\ 
\end{tabular}

\vspace{8mm}


\textbf{\textsc{Submitted and Refereed Publications}} \\
\vspace{1mm}
\hspace*{5mm}First author and papers led by students: \\
\hspace*{5mm}(*** denotes student papers supervised by L.K.)
\begin{compactenum}
\item ``New Analysis Indicates No Evidence for Lunar Companion Orbiting Kepler-1625b"\\
\textbf{Kreidberg}, Luger, and Bedell, submitted to ApJL

\item``The Sub-Neptune Desert and Its Dependence on Stellar Type: Controlled by Lifetime X-Ray Irradiation"\\
****McDonald, \textbf{Kreidberg}, and Lopez, submitted to AJ 

\item ``Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103b from HST and Spitzer Phase Curve Observations"\\
\textbf{Kreidberg}, Line, Parmentier et al., 2018, \textit{AJ}, 156, 17

\item ``SPIDERMAN: an open-source code to model phase curves and secondary eclipses"\\
****Louden and \textbf{Kreidberg} 2018, MNRAS, 477, 2613 

\item ``Water, High Altitude Condensates, and Possible Methane Depletion in the Atmosphere of the Warm Neptune WASP-107b"\\
\textbf{Kreidberg}, Line, Thorngren et al. 2018, ApJL, 858, 6 

\item ``Exoplanet Atmosphere Measurements from Transmission Spectroscopy and other Planet-Star Combined Light Observations"\\
\textbf{Kreidberg} 2017, Handbook of Exoplanets,  arXiv:1709.05941

\item ``Prospects for Characterizing the Atmosphere of Proxima Centauri b"\\
\textbf{Kreidberg} \& Loeb, 2016, \textit{ApJL}, 832, 12 

\item ``A Detection of Water in the Transmission Spectrum of the Hot Jupiter WASP-12b and Implications for its Atmospheric Composition"\\
\textbf{Kreidberg}, Line,  Bean, et al., 2015, \textit{ApJ}, 814, 66

\item ``\texttt{batman}: BAsic Transit Model cAlculatioN in Python"\\
\textbf{Kreidberg} 2015, \textit{PASP}, 127, 1161 

\item ``A Precise Water Abundance Measurement for the Hot Jupiter WASP-43"\\
\textbf{Kreidberg}, Bean, D\'esert, et al. 2014, \textit{ApJL}, 793, 27

\item ``Clouds in the Atmosphere of the Super-Earth Exoplanet GJ 1214b"\\
\textbf{Kreidberg}, Bean, D\'esert, et al. 2014, \textit{Nature}, 505, 69

\item ``Mass Measurements of Black Holes in X-Ray Transients:  Is There a Mass Gap?"\\
\textbf{Kreidberg}, Bailyn, Farr, \& Kalogera 2012, \textit{ApJ}, 757, 36
\end{compactenum}

\vspace{3mm}
\hspace*{5mm}Co-authored:
\begin{compactenum}
\setcounter{enumi}{12}
\item ``HD 202772A b: A Transiting Hot Jupiter around a Bright, Mildly Evolved Star in a Visual Binary Discovered by TESS"\\
    Wang, Jones, Shporer, et al. [including \textbf{Kreidberg}], 2019, AJ, 157, 51

\item ``Detection of Helium in the Atmosphere of the Exo-Neptune HAT-P-11b"\\
Mansfield, Bean, Oklop\v{c}i\'{c}, \textbf{Kreidberg}, et al. 2018, ApJL, 868, 34

\item ``A Framework for Prioritizing the TESS Planetary Candidates Most Amenable to Atmospheric Characterization"\\
   Kempton, Bean, Louie, et al. [including \textbf{Kreidberg}], 2018, PASP, 130, 4401 

\item  ``The Transiting Exoplanet Community Early Release Science Program for \textit{JWST}"\\
    Bean, Stevenson, Batalha, et al. [including \textbf{Kreidberg}], submitted to PASP, arXiv:1803.04985

\item ``Helium in the eroding atmosphere of an exoplanet"\\
    Spake, Sing, Evans, et al. [including \textbf{Kreidberg}] 2018, \textit{Nature}, 557, 68

\item ``From thermal dissociation to condensation in the atmospheres of extremely hot Jupiters: WASP-121b into context"\\
	Parmentier, Line, Bean, et al. [including \textbf{Kreidberg}], 2018, \textit{A\&A}, 617, 110

\item ``Two Warm, Low-Density Sub-Jovian Planets Orbiting Bright Stars in K2 Campaigns 13 and 14"
	Yu, Rodriguez, Crossfield, et al. [including \textbf{Kreidberg}], 2018, \textit{AJ}, 156, 127 

\item ``A HST/WFC3 Thermal Emission Spectrum of the Hot Jupiter HAT-P-7b"\\
Mansfield, Bean, Line, et al. [including \textbf{Kreidberg}], 2018, \textit{AJ}, 156, 10

\item ``H- Opacity and Water Dissociation in the Dayside Atmosphere of the Very Hot Gas Giant WASP-18b"\\
	Arcangeli, D\'{e}sert, et al. [including \textbf{Kreidberg}] 2018, \textit{ApJL}, 855, 30 

\item ``An ultra-short period rocky super-Earth with a secondary eclipse and a Neptune-like companion around K2-141"\\
Malavolta, Mayo, et al. [including \textbf{Kreidberg}] 2018, \textit{AJ}, 155, 107 

\item ``Observing the Atmospheres of Known Temperate Earth-sized Planets with JWST"\\
Morley, \textbf{Kreidberg}, et al. 2017, ApJ, 850, 121 

\item ``Trends in Atmospheric Properties of Neptune-Size Exoplanets"\\
Crossfield and \textbf{Kreidberg} 2017, \textit{AJ}, 154, 261 

\item ``Quantifying the Impact of Spectral Coverage on the Retrieval of Molecular Abundances from Exoplanet Transmission Spectra"\\
Chapman, Zellem, Line, et al. [including \textbf{Kreidberg}] 2017, \textit{PASP}, 129, 980

\item ``Determining Empirical Stellar Masses and Radii Using Transits and Gaia Parallaxes as Illustrated by Spitzer Observations of KELT-11b"\\
Beatty, Stevens, Collins, et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 154, 25 

\item ``A Multi-planet System Transiting the V = 9 Rapidly Rotating F-Star HD 106315"\\
Rodriguez, Zhou, Vanderburg, et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 153, 256

\item ``HELIOS: An Open-Source, GPU-Accelerated Radiative Transfer Code for Self-Consistent Exoplanetary Atmospheres"\\
Malik, Grosheintz,  et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 153, 56 

\item ``Spitzer Phase Curve Constraints for WASP-43b at 3.6 and 4.5 microns"\\
Stevenson, Line, Bean, et al. [including \textbf{Kreidberg}] 2016, \textit{AJ}, 153, 68 

\item ``Near-IR Emission Spectrum of WASP-103b using Hubble Space Telescope/Wide Field Camera 3"\\
Cartier, Beatty, Zhao, et al. [including \textbf{Kreidberg}] 2017, \textit{AJ}, 153, 34


\item ``No Thermal Inversion and a Solar Water Abundance for the Hot Jupiter HD 209458b from HST WFC3 Emission Spectroscopy"\\
Line, Stevenson, Bean, et al. [including \textbf{Kreidberg}], 2016, \textit{AJ}, 152, 203 

\item ``The Impact of Non-uniform Thermal Structure on the Interpretation of Exoplanet Emission Spectra"\\
Feng, Line, Fortney, et al. [including \textbf{Kreidberg}], 2016, \textit{ApJ}, 829, 52

\item ``Transiting Exoplanet Studies and Community Targets for JWST's ERS Program"\\
Stevenson, Lewis, Bean, et al. [including \textbf{Kreidberg}], 2016, \textit{PASP}, 128, 967 

\item ``The Atmospheric Circulation of the Hot Jupiter WASP-43b" \\
Kataria, Showman, Fortney, et al. [including \textbf{Kreidberg}] 2015, \textit{ApJ}, 801, 86

\item ``Observations of Transiting Exoplanets with the James Webb Space Telescope (JWST)"\\
Beichman, Benneke, Knutson, et al. [including \textbf{Kreidberg}] 2014, \textit{PASP}, 126, 1134

\item ``Thermal structure of an exoplanet atmosphere from phase-resolved emission spectroscopy"\\
Stevenson, D\'esert, Line, et al. [including \textbf{Kreidberg}] 2014, \textit{Science}, 346, 838

\item ``A Hubble Space Telescope Search for a Sub-Earth-sized Exoplanet in the GJ 436 System"\\
Stevenson, Bean, Fabrycky, \& \textbf{Kreidberg} 2014, \textit{ApJ}, 796, 32

\item ``HST Near-IR Transmission Spectroscopy of the Super-Earth HD 97658b"\\
Knutson, Dragomir, \textbf{Kreidberg}, et al. 2014, \textit{ApJ}, 794, 155

\item ``Transmission Spectroscopy of the Hot Jupiter WASP-12b from 0.7 to 5 $\mu$m"\\
Stevenson, Bean, Seifahrt, et al. [including \textbf{Kreidberg}] 2014, \textit{AJ}, 147, 161

\item ``The Mass Distribution of Stellar-Mass Black Holes"\\
Farr, Sravan, Cantrell, \textbf{Kreidberg} et al. 2011, \textit{ApJ}, 741, 103
\end{compactenum}
\vspace{5mm}

\textbf{\textsc{White Papers and Research Notes}} 
\vspace{1mm}
\begin{compactenum}
\item ``Non-Detection of a Helium Exosphere for the Hot Jupiter WASP-12b"\\
\textbf{Kreidberg} and Oklop\v{c}i\'{c} 2018, \textit{RNAAS}, 2, 44

\item ``Understanding Stellar Contamination in Exoplanet Transmission Spectra as an Essential Step in Small Planet Characterization"\\
Apai, Rackham, et al. [including \textbf{Kreidberg}] 2018, submitted to the National Academy of Sciences Committee on Exoplanet Science Strategy, arXiv:1803.08708

\item ``Additional Exoplanet Science Enabled by FINESSE"\\
Zellem, Fortney, et al. [including \textbf{Kreidberg}] 2018, submitted to the
National Academy of Sciences Committee on Exoplanet Science Strategy, arXiv:1803.07163

\item ``The Science Case for an Extended Spitzer Mission"\\
Yee, Fazio, et al. [including \textbf{Kreidberg}] 2017, arXiv:1710.04194
\end{compactenum}


\end{document}
